Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-27 paper/lncsFormat.tex
remove pages in the bib file
merge two illustration figures into a integrated one

\intextsep=5pt plus 3pt minus 1pt
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
    \centering
    \includegraphics[width=.82\columnwidth]{img/NSDetectorExample.pdf}
    \intextsep=0pt plus 3pt minus 1pt
    \caption{\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.}
    \label{fig:modelDesc}
\end{figure}

@@

\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the \textit{class}\(\rightarrow\)\textit{subclass} relations in the knowledge base. 
Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
As \(G^{(0)}\) is not a Directed Acyclic Graph originally\cite{faralli2015large}, we remove the cycles according to nodes' PageRank-HITS\cite{Yan:2015wq} score.
Specifically, the edges \textit{class}\(\rightarrow\)\textit{subclass} are preserved only when the node \textit{class} has the higher PageRank-HITS score than the node \textit{subclass}, which is shown in the line \ref{alg:line2inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
After removing cycles, the taxonomy structure on the knowledge base is better represented by the directed acyclic graph \(G^{(0)'}\).
As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{Military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc. 
\begin{figure}[h]
    \centering
    \includegraphics[width=.82\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
    \label{fig:NSinitializaton}
\end{figure}

@@

\textbf{Page-Content Map \(G^{(2)}\)}. 
For a specific Wikipedia dumps version, the edges \textit{page}\(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
There are a bulk of history information restored in the wiki text content.
In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.

>>>>

\intextsep=5pt plus 3pt minus 1pt
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
	\centering
    \label{fig:subfig} %% label for entire figure
        \subfigure[]{
                \includegraphics[width=.42\columnwidth]{img/NSDetectorExample.pdf}
                \label{fig:modelDesc}

        }
        \subfigure[]{
                \includegraphics[width=.42\columnwidth]{img/initializationExample.pdf}
                \label{fig:NSinitializaton}
        }
        \caption{(a)\textsc{LTDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{LTDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
\end{figure}

@@

\textbf{Taxonomy Graph \(G^{(0)}\)}. The directed edges in \(G^{(0)}\) represent the \textit{class}\(\rightarrow\)\textit{subclass} relations in the knowledge base. 
Taking Wikipedia for example (Figure \ref{fig:NSinitializaton}), the node \textit{Main topic classifications}\footnote{\url{https://en.wikipedia.org/wiki/Category:Main_topic_classifications}} has the subclass \textit{Society}, further contains the subclass \textit{Politics}, which is the ancestor of the subclass \textit{Military}.
As \(G^{(0)}\) is not a Directed Acyclic Graph originally\cite{faralli2015large}, we remove the cycles according to nodes' PageRank-HITS\cite{Yan:2015wq} score.
Specifically, the edges \textit{class}\(\rightarrow\)\textit{subclass} are preserved only when the node \textit{class} has the higher PageRank-HITS score than the node \textit{subclass}, which is shown in the line \ref{alg:line2inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}.
After removing cycles, the taxonomy structure on the knowledge base is better represented by the directed acyclic graph \(G^{(0)'}\).
As shown in line \ref{alg:line3inNormalStatesInit} of Algorithm \ref{alg:normalStatesInit}, by visiting the category \textit{Military} in the DAG \(G^{(0)'}\), the breadth-first traverse can reach its successor sub-category nodes such as \textit{Firearms}, \textit{The World Wars}, and \textit{World War II}, etc.

@@

\textbf{Page-Content Map \(G^{(2)}\)}. 
For a specific Wikipedia dumps version, the edges  \textit{page} \(\rightarrow\)\textit{content} in \(G^{(2)}\) define a one-to-one mapping.
There are a bulk of history information restored in the wiki text content.
In order to extract the key words in wiki page's content, which distinguish it from other pages, we use the chi-square statistics\cite{yang1997comparative}\cite{liu2009imbalanced} to measure the importance of each word for the specific page.
